Commutative Character Sheaves

### 2016-01-06 followup.tex
Working on symmetric classes

\title[Commutative Character Sheaves]{Commutative Character Sheaves on smooth group schemes over finite fields}
%with an application to geometric types for supercuspidal representations
\author{Clifton Cunningham}
\address{Department of Mathematics and Statistics, University of Calgary, 2500 University Drive Northwest, Calgary, AB, Canada, {T2N~1N4}.}
\email{cunning@math.ucalgary.ca}
\author{David Roe}
\address{Department of Mathematics, University of Pittsburgh, 301 Thackeray Hall, Pittsburgh, PA , United States, 15260.}
\email{roed.math@gmail.com}

@@

If $M$ is a $\bG$-module, then we say a class in the Galois cohomology group $\Hh^2(\bG, M)$
is \emph{symmetric} if it is represented by a symmetric $2$-cocycle.  Since every coboundary is symmetric,
either all cocycles in a given class will be symmetric or none will.  The connection between
commutative character sheaves and symmetric classes is given in the following lemma.
\todo{Define symmetric for element of $\Hh^2(E_G^\bullet)$.}

@@

@@

Suppose that $\cs{L}$ is a commutative character sheaf
with $\trFrob{\cs{L}} = 1$.  Then $S_G([\cs{L}])$ is in the image of $\Hh^2(\bG, \EEx)^\Weil{}$, so is cohomologous to
$[\alpha', 0]$.  Since $\alpha$ is symmetric and coboundaries are symmetric, $\alpha'$ is symmetric as well.
So by Lemma \ref{lem:symtriv}, $\alpha'$ is cohomologically trivial, and thus $[\cs{L}]$ is trivial as well.

@@

As proved in \cite{kim:07a}, all supercuspidal representations of unramified $p$-adic groups can be built from the data of \cite{yu:01a}*{\S 15}.
The type, in the sense of \cite{bushnell-kutzko:98a}, of the resulting supercuspidal representations can be constructed directly from the data. 
Let us refer to the types arising in this manner as {\it Yu types}.
In this section we show that every Yu type is geometrizable.
% in a sense which will be made clear below.

A Yu type is a pair $(\,^\circ K,\,^\circ \rho)$, where $\,^\circ K$ is a compact group and $\,^\circ \rho$ is a representation of $\,^\circ K$, with certain properties. 
In Section~\ref{ssec:review} we recall properties of $(\,^\circ K,\,^\circ \rho)$ which we allow us, in Section~\ref{ssec:geometrization}, to find a pair $(G, \mathcal{F})$ where $G$ is a group scheme over $\Fq$ and $\mathcal{F}$ is a virtual constructible sheaf $\ell$-adic sheaf on $G$ from which the character of $\,^\circ \rho$ can be recovered using the trace of Frobenius.

@@

Every Yu type $(\,^\circ K,\,^\circ \rho)$ may be constructed directly from the following information, derived from a Yu datum:
\begin{enumerate}
\item[(0)] a compact group $\,^\circ K$;
\item[(1)] compact open subgroups $J^i\subset \,^\circ K$, for $i=0, \ldots d$, such that \[\,^\circ K = J^0\cdots J^d;\]
\item[(2)] a continuous representation $\varpi_0$ of $J^0$, inflated from ...
\item[(3)] a quasicharacter $\varphi_i : J^0\cdots J^i \to \CC^\times$, for $i=0, \ldots d$.
\end{enumerate}
These representations $(\sigma_0, \varphi_0, \ldots , \varphi_d)$ enjoy certain properties, which allow Yu to construct, for $i=0, \ldots, d-1$, further:
\begin{enumerate}
\item[(4)] a quotient $J^{i+1} \to V_{i+1}$ to a finite abelian group, and the structure of a $\Fq$-vector space on $V_{i+1}$, compatible with the abelian group structure above;
\item[(5)] a symplectic pairing $\langle\ ,\ \rangle_{i+1} : V_{i+1}\times V_{i+1} \to C_{i+1}$, where $C_{i+1}$ is a one-dimensional vector space over $\Fq$;
\item[(6)] an additive character $\psi_{i+1} : C_{i+1} \to \EEx$;
\item[(7)] a group homomorphism $\,^\circ f_i : J^0 \cdots J^i \to \Sp(V_{i+1})$;
\item[(8)] a quotient $J^{i+1} \to H^{i+1}$, where $H^{i+1}$ is a Heisenberg $p$-group;
\item[(9)] an isomorphism $j_{i+1} : H^{i+1} \to V_{i+1}^\sharp$, where $V_{i+1}^\sharp$ is the Heisenberg group determined by $(V_{i+1}, \langle\ ,\ \rangle_{i+1}, C_{i+1}, \psi_{i+1})$.
%\end{enumerate}
\item[(10)]The pair $(f_i, j_{i+1})$ is a symplectic action of $J^0\cdots J^i$ on $H^{i+1}$ in the sense of \cite{yu:construction}, so, together with the quotient $J^{i+1} \to H^{i+1}$, it defines a group homomorphism 
\begin{equation}\label{eq:symaction}
\begin{tikzcd}
h_{i+1} : (J^0\cdots J^i)\ltimes J^{i+1} \arrow{r} 
%& (J^0\cdots J^i)\ltimes H^{i+1} \arrow{r} 
& \Sp(V_{i+1})\ltimes V_{i+1}^\sharp.
\end{tikzcd}
\end{equation}
\end{enumerate}

From this information, Yu constructs 
a representation $\,^\circ \rho_i$ of $J^0\cdots J^i$, for each $i=0, \ldots, d$, such that $\,^\circ \rho_d = \,^\circ \rho$,
constructed as follows.
%\end{enumerate}
%We will need some more detail about the construction of the representations $\,^\circ \rho^i$, so we review it below.
%
We will need some detail about this construction,   so we review it here.

%Let $\varpi_1$ be the Heisenberg representation of the Heisenberg group $V_1^\sharp$, with central character $\psi_1$.
%Let $\varrho_1$ be the Weil representation of $\Sp(V_1)$ with the same representation space as $\omega_1$.
Let $\omega_{i+1}$ be the Heisenberg representation of the Heisenberg group $V_{i+1}^\sharp$.
This determines the Weil representation $W_{i+1}$ on the same representation space as the Heisenberg representation of $V_{i+1}^\sharp$.
Let $W_{i+1} \ltimes \omega_{i+1}$ be the Heisenberg-Weil representation of the Jacobi group $\Sp(V_{i+1})\ltimes V_{i+1}^\sharp$.
\[
\begin{tikzcd}
\  & J^{i+1} \arrow{d} & \\
\Sp(V_{i+1}) \ltimes V_{i+1}^\sharp & \arrow{l}[swap]{h_{i+1}} (J^0 \cdots J^i) \ltimes J^{i+1} \arrow{r} \arrow{d} & J^0 \cdots J^i J^{i+1}\\
& J^0 \cdots J^i & 
\end{tikzcd}
\]

Now $h_1^*(W_1\ltimes \omega_1)$ is a representation of $J^0\ltimes J^1$, determined by the quasicharacter $\varphi_1$ of $J^1$. 
Write $\inf(\sigma_0)$ for the representation of $J^0 \ltimes J^1$ obtained by pulling back $\sigma_0$ along $J^0 \ltimes J^1 \to J^0$. 
By \cite{yu:01a}*{}, the representation 
$h_1^*(\omega_1) \otimes \varphi_1 \otimes \inf(\sigma_0)$ of $J^0 \ltimes J^1$ is trivial on $(J^0 \ltimes 1) \cap (1 \ltimes J^1)$, so $h_1^*(\omega_1) \otimes \varphi_2 \otimes\inf(\sigma_0\otimes)$ descends to a representation $\,^\circ \rho_1$ of $J^0 J^1$.  
%
Likewise, the representation 
$h_{2}^*(\omega_{2}) \otimes \inf(\,^\circ \rho_1)$ of $J^0 \ltimes J^1$ is trivial on $(J^0 J^1 \ltimes 1) \cap (1 \ltimes J^2)$, so $h_2^*(\omega_2) \otimes \inf(\,^\circ \rho_1)$ descends to a representation $\,^\circ \rho_2$ of $J^0 J^1 J^2$.  
%
Continuing in this way, one constructs the representation $\,^\circ \rho_d$ of $J^0\cdots J^d$. 
%
The character of $\,^\circ \rho_d$ on $\,^\circ K = J^0\cdots J^d$ satisfies
\[
\trace(\,^\circ \rho_d)(k_0 \cdots k_d) = \sigma_0(k_0) \left( \varphi_0(k_0) \cdots \varphi_d(k_d) \right) ,
\]
for $k_i\in J^i$.

@@

By \cite{yu:models}*{Prop 10.2} there is a canonical affine smooth group scheme $\underline{G}$ of finite type over $\OK$ such that \[ 
\underline{G}(\OK)= \,^\circ K.
\] 
%
As explained in \cite{yu:03a}*{\S 10.4}, the group scheme $\underline{G}$ comes with the following auxilliary data:
\begin{enumerate}
\item[(Ji)]
	affine smooth group schemes $\underline{J}^i$, for $i=0, 1, \ldots, d$, together with morphisms $\underline{J}^i \to \underline{G}$ such that \[\underline{J}^i(\OK) = J^i,\]
\item[(Gj)] affine smooth group schemes $\underline{G}^{j}$, for $j=0, \ldots, d$, together with morphisms $\underline{G}^{j}\to \underline{G}$ such that 
\[
\underline{G}^{j}(\OK) = J^0\cdots J^i.
\] 
\end{enumerate}

\newcommand{\reductive}{{\operatorname{red}}}

With these group schemes, the other groups and group homomorphisms appearing in Section~\ref{ssec:review} may be put into the framework needed for geometrization.

Write $\underline{J}^{i+1}_\Fq$ for the special fibre $\underline{J}^{i+1}\times_S S_1$ of $\underline{J}^{i+1}$. 
The vector space $V_{i+1}$ may realized as the $\Fq$-points on a variety $U^{i+1}_\Fq$, where $U^{i+1}_\Fq$, appears as a quotient $J^{i+1}_\Fq \to U^{i+1}_\Fq$ of algebraic groups. Then the quotient $J^{i+1} \to V_{i+1}$ is realized as the composition
\[
\underline{J}^{i+1}(\OK) \to \underline{J}^{i+1}(\Fq) = \underline{J}^{i+1}_\Fq(\Fq) \to U^{i+1}_{\Fq}(\Fq) = V_{i+1}.
\]
Likewise, the Heisenberg p-group $H^{i+1}$ group may be realized as a quotient of algebraic groups, and $J^{i+1}\to H^{i+1}$ as the composition 
\[
\underline{J}^{i+1}(\OK) \to \underline{J}^{i+1}(\Fq) = \underline{J}^{i+1}_\Fq(\Fq) \to H^{i+1}_{\Fq}(\Fq) = H^{i+1}.
\]
Finally, the group homomorphism $\,^\circ f_i : J^0\cdots J^i \to \Sp(V_{i+1})$ may be made geometric in much the same way. Writing $\underline{G}^{i}_\Fq$ for the special fibre $\underline{G}^{i}\times_S S_1$ of $\underline{G}^{i}$, and writing $\underline{G}^{i,\reductive}_\Fq$ for the reductive quotient of $\underline{G}^{i}_\Fq$, there is a quotient of algebraic groups $\underline{G}^{i,\reductive}_\Fq \to W^{i+1}_\Fq$ so that $\,^\circ f_i : J^0\cdots J^i \to \Sp(V_{i+1})$ is realized as the composition
\[
\underline{G}^{i}(\OK) \to \underline{G}^{i}(\Fq) = \underline{G}^{i}_\Fq(\Fq) \to  \underline{G}^{i,\reductive}_\Fq(\Fq) \to W^{i+1}_{\Fq}(\Fq) = \Sp(V_{i+1}).
\]

Let us return to the list of Section~\ref{ssec:review} and consider how we have recast each part.
\begin{enumerate}
\item[(0)] The compact group $\,^\circ K$ is replaced by the smooth group scheme $\underline{G}$ over $\OK$.
\item[(1)] The compact open subgroups $J^i \hookrightarrow \,^\circ K$ are replaced by the morphisms $\underline{J}^i \to \underline{G}$ of smooth group schemes over $\OK$.
\item[(2)] The representation $\varpi_0$ is obtained by pullback from a representation $\sigma_0$ of $\underline{J}^{0,\reductive}_\Fq$, which makes use of the following morphisms of group schemes.
\[
\underline{J}^{0} \longleftarrow \underline{J}^{0}_\Fq \to \underline{J}^{0,\reductive}_\Fq.
\]
\item[(3)] The quasicharacters $\varphi_i : \underline{J}^i(\OK) \to \CC^\times$ have not yet been geometrized.
\item[(4)] The quotient $J^{i+1}\to V_{i+1}$ has been replaced with the following morphisms of group schemes.
\[
\underline{J}^{i+1} \longleftarrow \underline{J}^{i+1}_\Fq \to \underline{J}^{i+1,\reductive}_\Fq \to V_{i+1,\Fq}.
\]
\item[(5)] The symplectic pairing $\langle\ ,\ \rangle_{i+1} : V_{i+1}\times V_{i+1} \to C_{i+1}$ is given by 
\item[(6)]
\item[(7)] The group homomorphism $\,^\circ f_i : J^0 \cdots J^i \to \Sp(V_{i+1})$ has been replaced by the following morphisms of group schemes.
\[
\underline{G}^{i} \longleftarrow \underline{G}^{i}_\Fq \to \underline{G}^{i,\reductive}_\Fq \to \Sp(V_{i,\Fq}),
\]
and $\Sp(V_{i,\Fq})$ is itself a reductive algebraic group over $\Fq$.
\item[(8)] The quotient $J^{i+1} \to H^{i+1}$ has been replaced by the following morphisms of group schemes.
\[
\underline{J}^{i+1} \longleftarrow \underline{J}^{i+1}_\Fq \to H^{i+1}_\Fq.
\] 
\item[(9)]
The Heisenberg group $V_{i+1}^\sharp$ is replaced by a unipotent algebraic group $V_{i+1,\Fq}^\sharp$ over $\Fq$, and the group isomorphism $H^{i+1} \iso V_{i+1}^\sharp$ is replaced by an isomorphism $H^{i+1}_\Fq \iso V_{i+1,\Fq}^\sharp$ of algebraic groups over $\Fq$.
\item[(10)]

\end{enumerate}

Regarding this construction of the type $(\,^\circ  K,\,^\circ \rho)$, the paper \cite{yu:models} concludes with the following provocative observation.

\begin{quotation}
{\it Therefore, up to some linear characters, all the ingredient representations are on groups of
 the form $\underline{H}(\mathcal{O})$, where $\underline{H}$ is a smooth group scheme over $\mathcal{O}$, and the representations are inflated from $\underline{H}(\kappa)$. These results suggest that algebraic geometry and group schemes should play an
important role in the representation theory of $p$-adic groups.} \cite{yu:03a}
\end{quotation}
%
The objective of this section is to push this observation further by geometrizing the representation $\,^\circ \rho$ of $\underline{G}$.

@@

\begin{proposition}
Let $(V, \langle\ , \rangle, C, \psi)$ be a finite-dimensional vector space over $\Fq$ and . .  .
Let $V^\sharp$ be the geometric Heisenberg group determined by this and let $\omega$ be the Heisenberg representation of $V^\sharp$.
Let $W$ be the Weil representation of $\Sp(V)$ determined by $(\omega,V^\sharp)$. 
Let $W\ltimes \omega$ be the resulting representation of the Jacobi group $\Sp(V)\ltimes V^\sharp$.
Then there is a virtual $W\ltimes \omega$-equivariant constructible sheaf $\mathcal{W}$ on $\Sp(V)\ltimes V^\sharp$ such that $\trFrob{\mathcal{W}} = \trace(W\ltimes \omega)$.
\end{proposition}

%\begin{proof}
%We begin by geometrizing the Heisenberg representation $(\omega, V^\sharp)$ to $\mathcal{H}$.
%\end{proof}

The first step in the geometrization of the type $(\,^\circ K,\,^\circ \rho)$ is to replace $\,^\circ K$ with a group scheme $G$ over $\Fq$ so that $G(\Fq) = \,^\circ K$, canonically. 
Set $S = \Spec{\OK}$ and $S_n = \Spec{\OK/\mathfrak{m}^n}$, where $\mathfrak{m}_K$ is the maximal ideal in $\OK$, and $n$ is a positive integer $n$.
Let $G_n$ be the Greenberg transform of $\underline{G} \times_{S} S_n$.
Then $G_n$ is a smooth group scheme over $\Fq$ and 
\[
G_n(\Fq) = \underline{G}(\OK/\mathfrak{m}_K^n),
\]
canonically.
%
Let $G$ be the Greenberg transform of $\underline{G}$.
Then $G$ is a group scheme over $\Fq$ and 
\[
G(\Fq) = \,^\circ K,
\]
canonically.

>>>>

\title[Commutative Character Sheaves]{Commutative Character Sheaves}
%with an application to geometric types for supercuspidal representations
\author{Clifton Cunningham}
\address{Department of Mathematics and Statistics, University of Calgary, 2500 University Drive Northwest, Calgary, AB, Canada, {T2N~1N4}.}
\email{cunning@math.ucalgary.ca}
\author{David Roe}
\address{Department of Mathematics, University of Pittsburgh, 301 Thackeray Hall, Pittsburgh, PA , United States, 15260.}
\email{roed.math@gmail.com}

@@

Let $a \in Z^2(\bG, \EEx)$ correspond to $\alpha$.  We say that $[\alpha \oplus \beta] \in \Hh^2(E_G^\bullet)$
is \emph{symmetric} if $a(x,y) = a(y,x)$ for all $x,y \in \bG$.  This condition is well defined, since every
coboundary in $B^2(\bG, \EEx)$ is symmetric.  The connection between commutative character sheaves
and symmetric classes is given in the following lemma.

@@

We may similarly define a symmetric class in $\Hh^2(\bG, \EEx)$ to be one represented by a symmetric $2$-cocycle.
The following lemma will allow us to show that there are no invisible commutative character sheaves.

@@

Suppose that $\cs{L}$ is a commutative character sheaf with $\trFrob{\cs{L}} = 1$, and set $[\alpha, \beta] = S_G([\cs{L}])$.
Then $S_G([\cs{L}])$ is in the image of $\Hh^2(\bG, \EEx)^\Weil{}$, so is cohomologous to
$[\alpha', 0]$.  Since $\alpha$ is symmetric and coboundaries are symmetric, $\alpha'$ is symmetric as well.
So by Lemma \ref{lem:symtriv}, $\alpha'$ is cohomologically trivial, and thus $[\cs{L}]$ is trivial as well.

@@

As proved in \cite{kim:07a}, all supercuspidal representations of unramified $p$-adic groups can be built from the data of \cite{yu:01a}*{\S 15}.
The type, in the sense of \cite{bushnell-kutzko:98a}, of the resulting supercuspidal representations can be constructed directly from the data. 
Let us refer to the types arising in this manner as {\it Yu types}.
In this section we show that every Yu type is geometrizable, in a sense which will be made clear below.

A Yu type is a pair $(\,^\circ K,\,^\circ \rho)$, where $\,^\circ K$ is a compact group and $\,^\circ \rho$ is a representation of $\,^\circ K$, with certain properties. 
In Section~\ref{ssec:review} we recall properties of $(\,^\circ K,\,^\circ \rho)$ which we allow us, in Section~\ref{ssec:geometrization}, to find a pair $(G, \mathcal{F})$ where $G$ is a smooth group scheme over $\Fq$ and $\mathcal{F}$ is a virtual constructible sheaf $\ell$-adic sheaf on $G$ from which the character of $\,^\circ \rho$ can be recovered using the trace of Frobenius.

@@

Every Yu type $(\,^\circ K,\,^\circ \rho)$ may be constructed directly from the following information, derived from a Yu datum:
\begin{enumerate}
\item compact open subgroups $J^i\subset \,^\circ K$, for $i=0, \ldots d$, such that \[\,^\circ K = J^0\cdots J^d;\]
\item a continuous representation $\sigma_0$ of $J^0$;
\item a quasicharacter $\varphi_i : J^i \to \CC^\times$, for $i=0, \ldots d$.
\end{enumerate}
These representations $(\sigma_0, \varphi_0, \ldots , \varphi_d)$ enjoy certain properties, which allow Yu to construct, for $i=0, \ldots, d-1$, further:
\begin{enumerate}
\item a quotient $J^{i+1} \to V_{i+1}$ to a finite abelian group, and the structure of a $\Fq$-vector space on $V_{i+1}$, compatible with the abelian group structure above;
\item a symplectic pairing $\langle\ ,\ \rangle_{i+1} : V_{i+1}\times V_{i+1} \to C_{i+1}$, where $C_{i+1}$ is a one-dimensional vector space over $\Fq$;
\item an additive character $\psi_{i+1} : C_{i+1} \to \EEx$;
\item a group homomorphism $\,^\circ f_i : J^0 \cdots J^i \to \Sp(V_{i+1})$;
\item a quotient $J^{i+1} \to H^{i+1}$, where $H^{i+1}$ is a Heisenberg $p$-group, together with an isomorphism $j_{i+1} : H^{i+1} \to V_{i+1}^\sharp$, where $V_{i+1}^\sharp$ is the Heisenberg group determined by $(V_{i+1}, \langle\ ,\ \rangle_{i+1}, C_{i+1}, \psi_{i+1})$.
\end{enumerate}
The pair $(f_i, j_{i+1})$ is a symplectic action of $J^0\cdots J^i$ on $H^{i+1}$, so it defines a group homomorphism 
\begin{equation}\label{eq:symaction}
\begin{tikzcd}
h_{i+1} : (J^0\cdots J^i)\ltimes J^{i+1} \arrow{r} & (J^0\cdots J^i)\ltimes H^{i+1} \arrow{r} & \Sp(V_{i+1})\ltimes V_{i+1}^\sharp.
\end{tikzcd}
\end{equation}
%

From this information, Yu constructs a representation $\,^\circ \rho_i$ of $J^0\cdots J^i$, for each $i=0, \ldots, d$, such that $\,^\circ \rho_d = \,^\circ \rho$. We will need some detail about this construction, so we will review it here.
%Let $\varpi_1$ be the Heisenberg representation of the Heisenberg group $V_1^\sharp$, with central character $\psi_1$.
%Let $\varrho_1$ be the Weil representation of $\Sp(V_1)$ with the same representation space as $\omega_1$.
Let $\omega_{i+1}$ be the Heisenberg-Weil representation of the Jacobi group $\Sp(V_{i+1})\ltimes V_{i+1}^\sharp$, with the same representation space as the Heisenberg representation of the Heisenberg group $V_{i+1}^\sharp$.
\[
\begin{tikzcd}
\  & J^{i+1} \arrow{d} & \\
Sp(V_{i+1}) \ltimes V_{i+1}^\sharp & \arrow{l}[swap]{h_1} (J^0 \cdots J^i) \ltimes J^{i+1} \arrow{r} \arrow{d} & J^0 \cdots J^i J^{i+1}\\
& (J^0 \cdots J^i) & 
\end{tikzcd}
\]
Then $h_1^*(\omega_1)$ is a representation of $J^0\ltimes J^1$, determined by the quasicharacter $\varphi_1$ of $J^1$. 
Write $\inf(\sigma_0\otimes \varphi_0)$ for the representation of $J^0 \ltimes J^1$ obtained by pulling back $\sigma_0\otimes \varphi_0$ along $J^0 \ltimes J^1 \to J^0$. 
By \cite{yu:01a}*{}, the representation 
$h_1^*(\omega_1) \otimes \inf(\sigma_0\otimes \varphi_0)$ of $J^0 \ltimes J^1$ is trivial on $(J^0 \ltimes 1) \cap (1 \ltimes J^1)$, so $h_1^*(\omega_1) \otimes \inf(\sigma_0\otimes \varphi_0)$ descends to a representation $\,^\circ \rho_1$ of $J^0 J^1$.  
%
As above, the representation 
$h_{2}^*(\omega_{2}) \otimes \inf(\,^\circ \rho_1)$ of $J^0 \ltimes J^1$ is trivial on $(J^0 J^1 \ltimes 1) \cap (1 \ltimes J^2)$, so $h_2^*(\omega_2) \otimes \inf(\,^\circ \rho_1)$ descends to a representation $\,^\circ \rho_2$ of $J^0 J^1 J^2$.  
Continuing in this way, one constructs the representation $\,^\circ \rho_d$ of $J^0\cdots J^d$.

The character of $\,^\circ \rho_d$ on $J^0\cdots J^d$ satisfies
\[
\trace(\,^\circ \rho_d)(k_0 \cdots k_d) = \sigma_0(k_0) \left( \varphi_0(k_0) \cdots \varphi_d(k_d) \right) ,
\]
with ...

@@

The first step in the geometrization of the type $(\,^\circ K,\,^\circ \rho)$ is to replace $\,^\circ K$ with a group scheme $G$ over $\Fq$ so that $G(\Fq) = \,^\circ K$, canonically. 
By \cite{yu:03a}*{Prop 10.2} there is a canonical affine smooth group scheme $\underline{G}$ of finite type over $\OK$ such that \[\underline{G}(\OK)= \,^\circ K\] 
For every positive integer $n$, let $G_n$ be the Greenberg transform of $\underline{G} \times_{\Spec{\OK}} \Spec{\OK/\mathfrak{m}_K^n}$, where $\mathfrak{m}_K$ is the maximal ideal in $\OK$.
Then $G_n$ is a smooth group scheme over $\Fq$ and $G_n(\Fq) = \underline{G}(\OK/\mathfrak{m}_K^n)$, canonically.
Let $G$ be the Greenberg transform of $\underline{G}$.
Then $G$ is a group scheme over $\Fq$ and $G(\Fq) = \underline{G}(\OK) = \,^\circ K$, canonically.

In order to complete the geometrization of the type $(\,^\circ K,\,^\circ \rho)$, we will need more smooth models.
Fortunately, as above, Yu has already done the heavy work.
%
As explained in \cite{yu:03a}*{\S 10.4}, the
the group scheme $\underline{G}$ comes with the following auxillary data:
\begin{enumerate}
\item[(Ji)]
	affine smooth group schemes $\underline{J}^i$, for $i=0, 1, \ldots, d$, together with morphisms $\underline{J}^i \to \underline{G}$ such that \[\underline{J}^i(\OK) = J^i,\]
\item[(Gj)] affine smooth group schemes $\underline{G}^{j}$, for $j=0, \ldots, d$, together with morphisms $\underline{G}^{j}\to \underline{G}$ such that 
\[
\underline{G}^{j}(\OK) = J^0\cdots J^i.
\] 
\end{enumerate}

Moreover, the quotient

Regarding this construction of the type $(\,^\circ  K,\,^\circ \rho)$, the paper \cite{yu:03a} concludes with the following provocative observation.
\begin{quotation}
{\it Therefore, up to some linear characters, all the ingredient representations are on groups of
 the form $\underline{H}(\mathcal{O})$, where $\underline{H}$ is a smooth group scheme over $\mathcal{O}$, and the representations are inflated from $\underline{H}(\kappa)$. These results suggest that algebraic geometry and group schemes should play an
important role in the representation theory of $p$-adic groups.} \cite{yu:03a}
\end{quotation}
%
The objective of this section is to push this observation further by geometrizing the representation $\,^\circ \rho$ of $\underline{G}$.

@@
